Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: significant improvement in the dark energy figure of merit

### 2017-11-03 Draft/Draft1.4.tex
minor changes

\author{Xiao-Dong Li,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cristiano G. Sabiu,}
\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
\author{Changbom Park,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Yuting Wang, Gong-bo Zhao}
\affil{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
\author{Hyunbae Park, Arman Shafieloo,}
\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
\author{Juhan Kim,}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}
\author{and Sungwook E. Hong}
\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}

@@

\begin{abstract}
We use the anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
%Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
%while improving upon earlier works \citep{Li2016},
%we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
%This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
%allowing for competitive and unbiased constrains to be placed on cosmological parameters.
The Alcock-Paczynski (AP) test was performed via the redshift dependence of clustering on scales of 6--40 $h^{-1}\rm Mpc$.
We improve the methodology of \cite{Li2016} by significantly reducing its computation time. 
This enables us to efficiently explore three or more cosmological parameters.
We then apply the improved method on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$.
In combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, we obtain
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30-40\%,
%and reduces the area of $w_0-w_a$ contour by 50\%.
and improves the dark energy figure of merit by a factor of 2. 
We checked the robustness of the results.
%The AP method may %be combined with the standard BAO method,
%greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

@@

The  origin  of  the late-time accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
Theoretical explanations for this phenomena are many and range from a non-zero  vacuum energy and evolving  scalar  fields  remnant  from  the  big  bang, 
to modifications of Einstein's General Relativity\cite{2012IJMPD..2130002Y}. 
Considering the wealth of theoretical explanations, 
it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
differentiate between competing models.

@@

The symmetry properties of galaxy pairs\cite{Marinoni2010}  could also be used to probe the AP effect;
however, since the peculiar velocity distorts the redshifts and changes the apparent tilt angles of galaxy pairs,
this method is also seriously limited by RSD \citep{Jennings2011}.

In an effort to minimize RSD contamination, the shape of void regions\cite{Ryden1995,LavausWandelt1995}  has been 
proposed as an AP probe. This approach has the advantage that the void regions are easier to model compared with dense regions, but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve competitive constraints \citep{Qingqing2016}.

@@

Previously, we proposed to use the {\it redshift dependence} of the AP distortion\cite{Li2014} as a way of mitigating the RSD effect. The clustering anisotropies produced by RSD are, although large, close to uniform in magnitude over a wide range in redshift.  However, if cosmological parameters are incorrectly chosen resulting in an AP effect, 
the anisotropy in the clustering signal has a clear redshift dependence
(as an illustration, Figure \ref{fig_xy} shows how the shape distortion of objects varies with distance (i.e., redshift) 
when incorrect cosmologies are used to infer distances).
In a later work\cite{Li2015}, we developed an AP methodology 
that utilizes the redshift dependence of the galaxy 2-point correlation function (2pCF), 
measured as a function of angle between the galaxy pair and line-of-sight (LoS).

@@

In this paper, we continue to develop our previous methodology and proceed to infer the constraints on dynamical dark energy. 
We will present a slightly improved methodology to that of our previous work\citep{Li2016}, 
allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
The methodology we will present here, can be applied to any model of dynamical dark energy, 
or indeed any appropriately chosen parametric or non-parametric decomposition of the cosmic expansion history. 
However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization\cite{CPL_CP,CPL_L},
\begin{equation}
w(z) = w_0 + w_a (1-a) = w_0 + w_a \frac{z}{1+z}.
\end{equation}
This parametrization characterizes dark energy equation-of-state (EoS) by two free parameters.
$w_0$ determines the present-day value, while parameter $w_a$ characterizes the first-order derivative of $w$ with respect to $a$. 
The possible redshift evolution of dark energy EoS is not considered in the analysis of \cite{Li2016}.

The CPL parametrization has many obvious advantages, for instance, a manageable parameter space, 
the bounded behavior at high redshift, 
and the ability to accurately reconstruct many dark energy theories\cite{CPL_L}. 
So it was widely used in the literature to reconstruct dark energy from observations.
The constraining power is usually quantified by the DETF (Dark Energy Task Force) \cite{DETF} figure of merit, 
defined as the reciprocal of the area of the error ellipse enclosing the 95\% confidence limit (CL) in the $w_0-w_a$ plane. 
Figure \ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
So we expect these two parameters effectively constrained by our method.

@@

The spectroscopic galaxy sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
the LOWZ sample, designed as an extension of the SDSS-I/II luminous red galaxy sample to $z\approx 0.4$ and fainter luminosities,
and the CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$),
targeted to be an approximately stellar mass limited sample of massive, luminous galaxies \cite{Reidetal:2016}.
In the clustering analysis we use 1,133,326 galaxies, split into six, non-overlapping redshift bins, 
$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
The number density of galaxies and the redshift binning scheme is plotted in the left panel of Figure \ref{fig_TpCF}.

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=6.5cm]{fig_nbar.eps}
   \includegraphics[width=9.0cm,]{fig_2pcf.eps}
   }
   \caption{\label{fig_TpCF}
   Splitting the SDSS galaxies into six redshift bins, and measuring the correlation function
   (similar figures already presented in \cite{Li2016}).
   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
   The vertical dashed lines define the six redshift bins that are used to cut the samples.
   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
   }
\end{figure*}

\begin{figure*}
   \centering{
   \includegraphics[width=16cm]{fig_smu.eps}
%   \includegraphics[width=10.5cm]{fig_comp.eps}
   }
   \caption{\label{fig_method}
   Mapping $\xi(s,\mu)$ from the fiducial cosmology (taken as the $\Omega_m=0.26$ $\Lambda$CDM cosmology) to other cosmologies. 
 The number counts are measured in the fiducial cosmology in the blue dashed grid.
 In the four cosmologies with $(w_0,w_a) = (-1.5,0),\ (-0.5,0),\ (-1,2)\ \rm and\ (-1,-2)$,
 %due to the distortion of geometry,
 according to Equation \ref{eq:smumap},
 the distribution of measured number counts in $(s, \mu)$ space becomes the red solid grid,
 To ensure the accuracy, we count the number of pairs in 5 times smaller pixels (the small red pixels), 
 and group them together to infer the values of $\xi(s, \mu)$ in blue dashed grid.
 For illustration purpose, 
  the blue and red grids are all 10 times sparser than the grids adopted in real analysis.
}
\end{figure*}

\begin{figure*}
   \centering{
   \includegraphics[width=8.5cm]{fig_comp.eps}
   \includegraphics[width=8.5cm]{fig_IO.eps}
   }
   \caption{\label{fig_Check}
 Left panel: Cosmological constraints from the BOSS DR12 galaxies, in the $\Omega_m$-$w_0$ plane. 
 The value of $w_a$ is fixed as zero.
 Results obtained using the precise 2pCFs (cyan filled) 
 and approximate 2pCFs (blue solid) agree with each other quite well.
 Right panel: Input-output test of the methodology using four sets of HR4 mock catalogues.
 The approximate 2pCFs are used in the analysis.
 The simulation cosmology, $\Omega_m=0.26$ $\Lambda$CDM, is marked by the black plus.
 The inferred cosmological constraints from the method, shown in the cygan contours, are consistent with the input cosmology.
   }
\end{figure*}

Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed.
%\footnote{These correlations were computed using the public code \texttt{KSTAT} \citep{kstat}.} 
as $\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds$, 
with $s_{\rm min}=6 h^{-1} {\rm Mpc},\ s_{\rm max}=40 h^{-1} {\rm Mpc}$.
We then normalize these {\em clustering shells} as 
$\hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}$
to nullify the amplitude information of the clustering signal, 
which is not associated with the Alcock-Paczynski test and is mostly sensitive to the galaxy bias.

The right panel of Figure \ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
The contour lines are not horizontal due to the effects of peculiar velocity,
and the RSD effect clearly manifest itself through the tilting of contour lines.
However, the shape of the tilted lines remain similar at different redshifts, a fact that enables us  to mitigate the RSD effect by focusing on the redshift dependence of the anisotropic clustering signal.
The ``correct'' cosmological model is selected by minimizing the amount of redshift evolution of $\hat\xi_{\Delta s}$,
via a $\chi^2$ function of 
\begin{equation}
 \chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2})
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering with respect to the lowest redshift bin,
while subtracting systematic effects:
\begin{eqnarray}
 {\bf p}(z_i,\mu_{j}) \equiv\ & \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right] \\ \nonumber
 &- \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}.
\end{eqnarray}
We use a number of $n_{\mu}$=20, 21, ... 25 bins for the value of $\hat\xi_{\Delta s}(\mu)$ at $0<\mu<\mu_{\rm max}$.
For the removal of fiber collision and the strong FoG effect near the LOS we take a cut $\mu_{\rm max} = 0.97$.

Systematics effects are estimated using mock catalogues derived from Horizon Run 4 (HR4) \cite{HR4},
an N-body simulation with box size $L={3150}$ $h^{-1}$Mpc, number of particles $6300^3$,   
initial redshift $z_{i}=100$, and WMAP5\citep{komatsu2011} cosmological parameters 
$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96). 
As presented in \cite{Li2016}, the value of $\left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}$
(mainly comes from redshift evolution of RSD and galaxy bias)
reaches 4-6\% at the highest redshift bin,
and is minor ($\lesssim2\%$) at the other redshift bins.
Mock galaxy samples are produced using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
The covariance matrix, ${\bf Cov}$, is computed from the 2,000 sets of MultiDark PATCHY mock catalogues \citep{MDPATCHY}.
The statistical bias and scattering in the likelihood function (due to the finite number of mocks in covariance estimation) 
are adequately corrected \citep{Hartlap,Percival2014}.

>>>>

\author{Xiao-Dong Li,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
\author{Cristiano G. Sabiu,}
\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
\author{Changbom Park,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
\author{Yuting Wang, Gong-bo Zhao}
\affil{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
\author{Hyunbae Park, Arman Shafieloo,}
\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
\author{Juhan Kim,}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}
\author{and Sungwook E. Hong}
\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}

@@

\begin{abstract}
We perform the Alcock-Paczynski (AP) test via the redshift dependence of clustering on scales of 6--40 $h^{-1}\rm Mpc$
to place constraints on the expansion history of the Universe.
We use 1,133,326 galaxies Sloan Digital Sky Survey Data Release 12 galaxies, spanning the redshift range $0.15<z<0.69$.
%Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
%while improving upon earlier works \citep{Li2016},
%we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
%This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
%allowing for competitive and unbiased constrains to be placed on cosmological parameters.
We improve the methodology of Li et al. to efficiently explore three or more cosmological parameters.
We then apply the improved method on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$.
In combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, we obtain
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30-40\%,
%and reduces the area of $w_0-w_a$ contour by 50\%.
and improves the dark energy figure of merit by a factor of 2. 
We checked the robustness of the results.
%The AP method may %be combined with the standard BAO method,
%greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

@@

%\begin{figure*}
%   \centering{
%   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
%   \includegraphics[height=6.5cm]{fig_nbar.eps}
%   \includegraphics[width=9.0cm,]{fig_2pcf.eps}
%   }
%   \caption{\label{fig_TpCF}
%   Splitting the SDSS galaxies into six redshift bins, and measuring the correlation function
%   (similar figures already presented in \cite{Li2016}).
%   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
%   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
%   The vertical dashed lines define the six redshift bins that are used to cut the samples.
%   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
%   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
%      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
%    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
%    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
%   }
%\end{figure*}

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[width=18cm]{fig_fan.eps}
   %\includegraphics[width=9.0cm]{fig_2pcf.eps}
   %\includegraphics[width=8.5cm]{fig_fan_2.eps}
   }
   \caption{\label{fig_fan}
   %We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
   A patch of BOSS DR12 glaxies located in the fan shape region $\rm 140^\circ < RA < 170 ^\circ$, $\rm 10^\circ < DEC < 13 ^\circ$.
   We split the sample into six non-overlapping redshift bins
   (marked by the light green rings) in order to probing the redshift evolution of anisotropic clustering.
   In the left and right panels, we plot the galaxies postions computed in two cosmologies: the $\Omega_m$=0.26 $\Lambda$CDM, 
   and a dynamical dark energy cosmology with $\Omega_m=0.26,\ w_0=-1,\ w_a=-2$.
   The redshifts and comoving distances (in unit of $h^{-1}\rm Mpc$) of the redshift bins are listed.
   %The shape of structures look different in these two cosmologies. 
   In the dynamical dark energy cosmology, we see apprent relative stretch of structures compared with the $\Lambda$CDM cosmology.
   The stretch is not significant in the first redshift bin, and becomes large in the higher redshift bins.
   We use this phenomena to discover the AP effect and place constraints on cosmologies.
   %By investigating how the anosotropy of galaxy distribution evolves in the six redshift bins,
   %we are able to distinguish different cosmologies.
   %The obtained galaxy distribution is different.
   %
   %The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
   %The vertical dashed lines define the six redshift bins that are used to cut the samples.
   %The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
   %Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
   %   in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
   % The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
   % The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
   }
\end{figure*}

The  origin  of  the late-time accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
Theoretical explanations for this phenomena are many and range from a non-zero  vacuum energy and evolving  scalar  fields  remnant  from  the  big  bang, 
to modifications of Einstein's General Relativity \citep{2012IJMPD..2130002Y}. 
Considering the wealth of theoretical explanations, 
it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
differentiate between competing models.

@@

The symmetry properties of galaxy pairs\citep{Marinoni2010}  could also be used to probe the AP effect;
however, since the peculiar velocity distorts the redshifts and changes the apparent tilt angles of galaxy pairs,
this method is also seriously limited by RSD \citep{Jennings2011}.

In an effort to minimize RSD contamination, the shape of void regions\citep{Ryden1995,LavausWandelt1995}  has been 
proposed as an AP probe. This approach has the advantage that the void regions are easier to model compared with dense regions, 
but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve competitive constraints \citep{Qingqing2016}.

@@

Previously, we proposed to use the {\it redshift dependence} of the AP distortion\citep{Li2014} as a way of mitigating the RSD effect. 
The clustering anisotropies produced by RSD are, although large, close to uniform in magnitude over a wide range in redshift.  
However, if cosmological parameters are incorrectly chosen resulting in an AP effect, 
the anisotropy in the clustering signal has a clear redshift dependence
(as an illustration, Figure \ref{fig_xy} shows how the shape distortion of objects varies with distance (i.e., redshift) 
when incorrect cosmologies are used to infer distances).
In \cite{Li2015}, we developed an AP methodology 
that utilizes the redshift dependence of the galaxy 2-point correlation function (2pCF), 
measured as a function of angle between the galaxy pair and line-of-sight (LoS).

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[width=8.95cm]{fig_xi_cosmo1.eps}
   \includegraphics[width=8.95cm]{fig_xi_cosmo2.eps}
   }
   \caption{\label{fig_xi}
   $\hat\xi_{\Delta s}(\mu)$ measured from BOSS DR12 galaxies, in six redshift bins (three in LOWZ and three in CMASS).
   This time we adopt the $\Omega_m=0.26$ $\Lambda$CDM cosmology and a more dark energy dominated cosmology, $\Omega_m=$0.11.
   The measurement in each redshift bin and the redshift evolution with respective to the measurement in first bin of LOWZ are shown.
   For comparison, the measurements in the HR4 mock catalogues (always in the $\Omega_m=0.26$ $\Lambda$CDM cosmology) are also plotted in green color.
   The simulation results can match the shape of curves measured from real observational data, 
   indicating that the FoG and Kaiser effects are well reproduced.
   In the cosmology $\Omega_m$=0.11 cosmology, the shapes of $\hat\xi_{\Delta s}(\mu)$ are different from the $\Omega_m=0.26$ cosmology results,
   and the amount of difference changes with redshift.
   A large redshift evolution of $\hat\xi_{\Delta s}(\mu)$ is detected in this cosmology, 
   indicating that it is not likely to be the underlying true cosmology of our universe.
   For the $\Omega_m$=0.11 cosmology, we also plot the approximate 2pCFs (red dashed lines) 
     inferred using the technique described in Sec. \ref{sec:approx_2pcf}.
   The error induced in the approximate procedure is $\lesssim0.5\%$.
   }
\end{figure*}

@@

In this paper, we continue to develop our previous methodology and proceed to infer the constraints on dynamical dark energy. 
We will present a slightly improved methodology to that of our previous work\citep{Li2016}, 
allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
The methodology we will present here, can be applied to any model of dynamical dark energy, 
or indeed any appropriately chosen parametric or non-parametric decomposition of the cosmic expansion history. 
However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization\citep{CPL_CP,CPL_L},
\begin{equation}
w(z) = w_0 + w_a (1-a) = w_0 + w_a \frac{z}{1+z}.
\end{equation}
This parametrization characterizes dark energy equation-of-state (EoS) by two free parameters.
$w_0$ determines the present-day value, while parameter $w_a$ characterizes the first-order derivative of $w$ with respect to $a$. 
The possible redshift evolution of dark energy EoS is not considered in the analysis of \cite{Li2016}.

The CPL parametrization has many obvious advantages, for instance, a manageable parameter space, 
the bounded behavior at high redshift, 
and the ability to accurately reconstruct many dark energy theories\citep{CPL_L}. 
So it was widely used in the literature to reconstruct dark energy from observations.
The constraining power is usually quantified by the DETF (Dark Energy Task Force) \citep{DETF} figure of merit, 
defined as the reciprocal of the area of the error ellipse enclosing the 95\% confidence limit (CL) in the $w_0-w_a$ plane. 
Figure \ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
So we expect these two parameters effectively constrained by our method.

@@

The spectroscopic galaxy sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
the LOWZ sample, designed as an extension of the SDSS-I/II luminous red galaxy sample to $z\approx 0.4$ and fainter luminosities,
and the CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$),
targeted to be an approximately stellar mass limited sample of massive, luminous galaxies \citep{Reidetal:2016}.
In the clustering analysis we use 1,133,326 galaxies, split into six, non-overlapping redshift bins, 
$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
The edges are determined so that the number of galaxies are roughly the same in different redshift bins 
(for LOWZ and CMASS samples, respectively).

%The number density of galaxies and the redshift binning scheme is plotted in the left panel of Figure \ref{fig_TpCF}.

Figure \ref{fig_fan} shows the positions of a patch of 10,976 BOSS DR12 glaxies,
computed in the $\Omega_m$=0.26 $\Lambda$CDM cosmology and a dynamical dark energy cosmology with $\Omega_m=0.26,\ w_0=-1,\ w_a=-2$.
The shape of structures look different in these two cosmologies. 
In the later cosmology, there is apprent stretch of structures, 
and the degree of compression becomes more significant in higher redshift bins.
By investigating how the anosotropy of galaxy distribution evolves in the six redshift bins,
we are able to distinguish this cosmology from the $\Lambda$CDM cosmology.

Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed as 
%\footnote{These correlations were computed using the public code \texttt{KSTAT} \citep{kstat}.} 
\begin{equation}
\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds,
\end{equation}
with $s_{\rm min}=6 h^{-1} {\rm Mpc},\ s_{\rm max}=40 h^{-1} {\rm Mpc}$.
We then normalize these {\em clustering shells} as 
\begin{equation}
\hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}
\end{equation}
to nullify the amplitude information of the clustering signal, 
which is not associated with the Alcock-Paczynski test and is mostly sensitive to the galaxy bias.
%The right panel of Figure \ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
%The contour lines are not horizontal due to the effects of peculiar velocity,
%and the RSD effect clearly manifest itself through the tilting of contour lines.
%However, the shape of the tilted lines remain similar at different redshifts, a fact that enables us  to mitigate the RSD effect by focusing on the redshift dependence of the anisotropic clustering signal.
The ``correct'' cosmological model is selected by minimizing the amount of redshift evolution of $\hat\xi_{\Delta s}$,
via a $\chi^2$ function of 
\begin{equation}
 \chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2})
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering with respect to the lowest redshift bin,
while subtracting systematic effects:
\begin{eqnarray}
 {\bf p}(z_i,\mu_{j}) \equiv\ & \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right] \\ \nonumber
 &- \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}.
\end{eqnarray}
We use a number of $n_{\mu}$=20, 21, ... 25 bins for the value of $\hat\xi_{\Delta s}(\mu)$ at $0<\mu<\mu_{\rm max}$.
For the removal of fiber collision and the strong finger of god (FoG) effect \citep{FOG} near the LOS we take a cut $\mu_{\rm max} = 0.97$.

Systematics effects are estimated using mock catalogues derived from Horizon Run 4 (HR4) \citep{HR4},
an N-body simulation with box size $L={3150}$ $h^{-1}$Mpc, number of particles $6300^3$,   
initial redshift $z_{i}=100$, and WMAP5\citep{komatsu2011} cosmological parameters 
$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96). 
Mock galaxy samples are produced using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
As presented in \cite{Li2016}, the value of $\left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}$
(mainly comes from redshift evolution of RSD and galaxy bias)
reaches 4-6\% at the highest redshift bin,
and is minor ($\lesssim2\%$) at the other redshift bins.

The covariance matrix, ${\bf Cov}$, is computed from the 2,000 sets of MultiDark PATCHY mock catalogues \citep{MDPATCHY}.
The statistical bias and scattering in the likelihood function (due to the finite number of mocks in covariance estimation) 
are adequately corrected \citep{Hartlap,Percival2014}.

The MultiDark PATCHY  mocks are produced using approximate gravity solvers and analytical-statistical biasing models.
They were calibrated to the BigMultiDark N-body simulation \citep{K2014}, which 
uses $3\,840^3$ particles in a volume of $(2.5h^{-1}\rm Gpc)^3$,
assuming a $\Lambda$CDM cosmology with 
$(\Omega_{b},\Omega_{m},h,\sigma_8,n_s)$  = (0.048206, 0.307115, 0.6777, 0.8288, 0.9611). 
%$\Omega_m = 0.307115$, $\Omega_b = 0.048206$, $\sigma_8 = 0.8288$, $n_s = 0.9611$, and $H_0 = 67.77 {\rm km}\ s^{-1} {\rm Mpc}^{-1}$.
The mock surveys can well reproduce the number density, 
selection function, survey geometry, and 2pCF measurement of the BOSS DR12 catalogues.
They have been adopted for statistical analysis of BOSS data in a series of works (see \cite{Alam2016} and references therein).

\begin{figure*}
   \centering{
   \includegraphics[width=12cm]{fig_smu.eps}
%   \includegraphics[width=10.5cm]{fig_comp.eps}
   }
   \caption{\label{fig_method}
   Mapping $\xi(s,\mu)$ from the fiducial cosmology (taken as the $\Omega_m=0.26$ $\Lambda$CDM cosmology) to other cosmologies. 
 The number counts are measured in the fiducial cosmology in the blue dashed grid.
 In the four cosmologies with $(w_0,w_a) = (-1.5,0),\ (-0.5,0),\ (-1,2)\ \rm and\ (-1,-2)$,
 %due to the distortion of geometry,
 according to Equation \ref{eq:smumap},
 the distribution of measured number counts in $(s, \mu)$ space becomes the red solid grid,
 To ensure the accuracy, we count the number of pairs in 5 times smaller pixels (the small red pixels), 
 and group them together to infer the values of $\xi(s, \mu)$ in blue dashed pixels.
 For illustration purpose, 
  the blue and red grids are all 10 times sparser than the grids adopted in the real analysis.
}
\end{figure*}

\begin{figure*}
   \centering{
   \includegraphics[width=8.5cm]{fig_IO.eps}
   \includegraphics[width=8.5cm]{fig_comp.eps}
   }
   \caption{\label{fig_Check}
 Left panel: Input-output test of the methodology using four sets of mock catalogues of BOSS DR12 galaxies constructed from the HR4 simulation.
 The approximate 2pCFs are adopted in the analysis.
 The simulation cosmology, $\Omega_m=0.26$ $\Lambda$CDM, is marked by the black plus.
 The inferred cosmological constraints from the method, shown in the cygan contours, are consistent with the input cosmology.
 Right panel: Cosmological constraints from the BOSS DR12 galaxies, assuming a $w$CDM cosmology 
 (i.e., the value of $w_a$ fixed as zero).
 Results obtained using the precise 2pCFs (cyan filled) 
 and approximate 2pCFs (red dashed) agree with each other quite well.
 The computation of precise 2pCFs is very expensive,
 so the comparison was done on a coarse grid of cosmological parameters with $\delta \Omega_m=0.025,\ \delta w=0.05$.
   }
\end{figure*}

As an illustration,
Figure \ref{fig_xi} shows how we us the above procedure to distinguish different cosmologies.
Here we plot the value of $\hat\xi_{\Delta s}(\mu)$, as long as its redshift evolution, 
measured from the BOSS DR12 galaxies in six redshift bins.
Two $\Lambda$CDM cosmologies are adopted, 
one with $\Omega_m=0.26$, and the other with obviously wrong value of $\Omega_m=0.11$.
